### 2016-07-08 filters-results.tex
adding new tasks

\section{Achieving FP-Security and Privacy}
\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not at all surprising, but it is the first result one would want in this area.}

>>>>

\section{Achieving FP-Security and Privacy}
\heading{FP-security. }
\begin{itemize}
\item FP-security/attacks on bigram/PRF-based double-hashing construction \tsnote{Animesh is doing this now}
\item FP-security/attacks on bigram/domain-separated PRF construction (see below, in Privacy section)
\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter''
\item FP-security/attacks on count-min sketch
\item ...
\end{itemize}

\heading{Privacy. }
\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not at all surprising, but it is the first result one would want in this area.}
